Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-07-03 patchy-selection-paper.tex
fixed typo

\paragraph{Other patches geometries}
Here we have studied circular patches of habitat at long distances from each other,
while real habitat is can be much more complex
-- archipelagos of patches of varying sizes, or connected by long, skinny corridors, for instance.
The work of \citet{cantrell1991diffusive} comes closest to a general theory of balanced polymorphisms in such habitats,
and it is possible that our techniques could be applied in their much more general setting,
as both are based, fundamentally, on branching process approximations.

>>>>

\paragraph{Other patch geometries}
Here we have studied circular patches of habitat at long distances from each other,
while real habitat is can be much more complex
-- archipelagos of patches of varying sizes, or connected by long, skinny corridors, for instance.
The work of \citet{cantrell1991diffusive} comes closest to a general theory of balanced polymorphisms in such habitats,
and it is possible that our techniques could be applied in their much more general setting,
as both are based, fundamentally, on branching process approximations.
